European or American? A re-examination of the transatlantic influence over the IMF

### 2025-09-02 manuscript/manuscript.qmd
Appendix: revise para 3 and 4

The required fiscal adjustment (RFA), however, shows inconsistent results. US influence correlates with significantly more stringent fiscal adjustment requirements in the short term ($p<0.05$ for T+1), while European influence is associated with more lenient short-term adjustment requirements ($p<0.1$). This is at odds with the findings on the number of (fiscal) conditions. Moreover, such patterns do not persist in the longer term (end year), where neither US nor European influence shows statistically significant effects. These mixed results suggest that while political alignment may influence the *number* of fiscal conditions imposed, it does not consistently affect the *stringency* of fiscal adjustment requirements over time. This echoes the findings of @guimaraes2021 and indicates that the relationship between political influence and the nature of conditionality is complex and warrants further investigation.

We note that these fiscal conditionality analyses are based on substantially smaller samples ($N\approxeq30$) and cover a more limited time period (1999-2012) than our main analyses. This reduction in sample size is due to the limited availability of disaggregated fiscal conditionality data. Consequently, these results should be interpreted with appropriate caution.

>>>>

The required fiscal adjustment (RFA), however, shows inconsistent results. US influence correlates with significantly more stringent fiscal adjustment requirements in the short term ($p<0.05$ for $T+1$), while European influence is associated with more lenient short-term adjustment requirements ($p<0.1$). This stands in contrast to the findings on the number of (fiscal) conditions. Moreover, these patterns do not persist in the longer term (end year), where neither US nor European influence shows statistically significant effects. These mixed results suggest that while political alignment may influence the *number* of fiscal conditions imposed, it does not consistently affect the *stringency* of fiscal adjustment requirements over time. This echoes the findings of @guimaraes2021 and indicates that the relationship between political influence and the nature of conditionality is complex and warrants further investigation.

We note that these fiscal conditionality analyses are based on substantially smaller samples ($N\approx 30$) and cover a more limited time period (1999–2012) than our main analyses. This reduction in sample size is due to the limited availability of disaggregated fiscal conditionality data. Consequently, these results should be interpreted with appropriate caution.
